Measuring Individual Partisan Harm in Redistricting

### 2021-09-11 paper/paper.Rmd
nj vars

```{r nj-maps, fig.cap="Baseline vote patterns, and two hypothetical gerrymanders.", fig.width=6.5, fig.height=3.5}
include_graphics(here("paper/figures/nj_maps.pdf"))
```

@@

>>>>

```{r nj-maps, fig.cap="Baseline vote patterns, and two hypothetical gerrymanders. Census-designated places are shaded in gray.", fig.width=6.5, fig.height=3.5}
include_graphics(here("paper/figures/nj_maps.pdf"))
```

@@

We sample 1,000 districting plans using the SMC algorithm of @mccartan2020, setting constraints to favor compact plans with district boundaries that tend to follow county lines.
For each of these sampled plans and the two gerrymanders, we calculate the utility, harm, and fairness measures, as well as the expected number of Democratic seats, the efficiency gap, partisan bias, and the mean-median score.
The distribution of these measures is shown in Figure \ref{fig:nj-vars}.

```{r nj-vars, fig.cap="Distributions of districting measures for simulated New Jersey distriting plans, the Republican gerrymander (red), and the Democratic gerrymander (blue).", fig.width=6.5, fig.height=3.25}
include_graphics(here("paper/figures/nj_vars.pdf"))
```
